Information Disclosure in Dynamic Innovation Contests

### 2025-06-05 paper/Paper.tex
update

\begin{theorem}[\citealt{ryvkin2022fight}]
In the Markov perfect equilibrium, the players’ efforts in state $m_{i(j)}(\tilde{y}_t, t) :\mathbb{R}\times[0, T)\to\mathbb{R}_+$ are given by
\begin{equation}\label{eq-equilibrium-effort}
m_{i(j)}(\tilde{y}_t, t) = \frac{e^{-z^2/2}}{\sqrt{2\pi\sigma^2(T-t)}}\cdot \frac{\sigma^2}{2}\left[\gamma(\rho_{i}) + \gamma(\rho_{j})\right]\left[1-\rho(z)^2\right]\left[1 \pm \rho(z)\right]
\end{equation}
where $z = \tilde{y}_t / (\sigma\sqrt{T-t})$, $\rho(z) = \gamma^{-1}\left(\Phi(z)\left[\gamma(\rho_{i})+\gamma(\rho_{j})\right]-\gamma(\rho_{j})\right)$ and 
\begin{equation*}
\gamma(u) = \frac{u}{1-u^2} + \frac{1}{2}\ln\frac{1+u}{1-u},\quad u\in(-1,1)
\end{equation*}
\begin{equation*}
\rho_{i} = \frac{e^{w_{i}}+e^{-w_{j}}-2}{e^{w_{i}}-e^{-w_{j}}},
\quad
\rho_{j} = \frac{e^{w_{j}}+e^{-w_{i}}-2}{e^{w_{j}}-e^{-w_{i}}},
\quad
w_{i(j)} = \frac{\theta}{\sigma^2 c_{i(j)}}.
\end{equation*}
Moreover, the total expected effort at time $t$, defined by $M(\tilde{y}_t, t) := \mathbb{E}\left[\int^T_t m_i(\tilde{y}_s, s) + m_j(\tilde{y}_s, s)ds\right]$, is given by $M(\tilde{y}_t, t) = \sigma \sqrt{T-t} q(z)$, where $q(z)$ is determined by the ordanary differential equation 
\begin{equation}
\begin{aligned}
&q''(z) + \left[4A_+(z)e^{-z^2/2}+z\right]q'(z) - q(z) + 4A_-(z)e^{-z^2/2} = 0\\
&A_-(z) = \frac{\gamma(\rho_1) + \gamma(\rho_2)}{2\sqrt{2\pi}}[1 - \rho(z)^2],
\quad A_+(z) = A_-(z)\rho(z)
\end{aligned}
\end{equation}
subject to the boundary conditions $q(z)\to0$ as $z\to\pm\infty$. 
Specifically, when $c_i = c_j$, we have $w_i = w_j = w$ and the total expected effort is reduced to 
\begin{equation}
M(\tilde{y}_t, t) = \frac{2w\sigma\sqrt{T-t}}{\sqrt{2\pi}}e^{-z^2/2} + o(w)
\end{equation}
\end{theorem}

The variables $w_{i(j)}$ measure the abilities of two players, while $\rho_{i(j)}$ normalizes $w_{i(j)}$ into the interval $(0, 1)$. 
Specifically, $\rho_{i(k)}$ and $w_{i(j)}$ are in a strictly increasing bijective relationship. 
It is not hard to see that function $\gamma(\cdot)$ is strictly increasing on $(-1,1)$, ranging from $-\infty$ to $+\infty$. 
The function $\rho(\cdot)$ is strictly increasing on $\mathbb{R}$, ranging from $-1$ to $1$. 
%% Forms
The equilibrium effort $m_{i(j)}$ can be represented to the product of two components:
the normal density function $\phi(y; 0, \sigma^2(T-t))$, which represents the probability density of a normal distribution with mean zero and variance $\sigma^2(T-t)$ evaluated at state $y$, and an amplitude factor $K_{i(j)}(z; \theta, \sigma, c_i, c_j) := \frac{\sigma^2}{2}\left[\gamma(\rho_{i}) + \gamma(\rho_{j})\right]\left[1-\rho(z)^2\right]\left[1 \pm \rho(z)\right]$. 
The normal density governs the concentration of competitive intensity over state, i.e., perceived output gap $\tilde{y}_t$, while the amplitude term $K_{i(j)}$ modulates the asymmetry (or skewness) of effort allocation between players.

It is also evident that the parameters $\theta$, $c_i$ and $c_j$ influence equilibrium effort exclusively through the amplitude component.
In contrast, the effect of $\sigma$ is more nuanced, as it enters both the normal density and amplitude terms. 
By the form of (\ref{eq-equilibrium-effort}), we can do some comparative analysis:

@@

To Do: Contest Design Rules

\begin{proposition}
...
\end{proposition}

>>>>

\begin{theorem}[\citealt{ryvkin2022fight}]
In the Markov perfect equilibrium, the players’ efforts in state $m_{i(j)}(\tilde{y}_t, t) :\mathbb{R}\times[0, T)\to\mathbb{R}_+$ are given by
\begin{equation}\label{eq-equilibrium-effort}
m_{i(j)}(\tilde{y}_t, t) = \frac{e^{-z^2/2}}{\sqrt{2\pi\sigma^2(T-t)}}\cdot \frac{\sigma^2}{2}\left[\gamma(\rho_{i}) + \gamma(\rho_{j})\right]\left[1-\rho(z)^2\right]\left[1 \pm \rho(z)\right]
\end{equation}
where $z = \tilde{y}_t / (\sigma\sqrt{T-t})$, $\rho(z) = \gamma^{-1}\left(\Phi(z)\left[\gamma(\rho_{i})+\gamma(\rho_{j})\right]-\gamma(\rho_{j})\right)$ and 
\begin{equation*}
\gamma(u) = \frac{u}{1-u^2} + \frac{1}{2}\ln\frac{1+u}{1-u},\quad u\in(-1,1)
\end{equation*}
\begin{equation*}
\rho_{i} = \frac{e^{w_{i}}+e^{-w_{j}}-2}{e^{w_{i}}-e^{-w_{j}}},
\quad
\rho_{j} = \frac{e^{w_{j}}+e^{-w_{i}}-2}{e^{w_{j}}-e^{-w_{i}}},
\quad
w_{i(j)} = \frac{\theta}{\sigma^2 c_{i(j)}}.
\end{equation*}
Moreover, the total expected effort at time $t$, defined by $M(\tilde{y}_t, t) := \mathbb{E}\left[\int^T_t m_i(\tilde{y}_s, s) + m_j(\tilde{y}_s, s)ds\right]$, is given by $M(\tilde{y}_t, t) = \sigma \sqrt{T-t} q(z)$, where $q(z)$ is determined by the ordanary differential equation 
\begin{equation}
\begin{aligned}
&q''(z) + \left[4A_+(z)e^{-z^2/2}+z\right]q'(z) - q(z) + 4A_-(z)e^{-z^2/2} = 0\\
&A_-(z) = \frac{\gamma(\rho_1) + \gamma(\rho_2)}{2\sqrt{2\pi}}[1 - \rho(z)^2],
\quad A_+(z) = A_-(z)\rho(z)
\end{aligned}
\end{equation}
subject to the boundary conditions $q(z)\to0$ as $z\to\pm\infty$. 
Specifically, when $c_i = c_j$, we have $w_i = w_j = w$ and the total expected effort is reduced to 
\begin{equation}\label{eq-totaleffort-reduced}
M(\tilde{y}_t, t) = \frac{2w\sigma\sqrt{T-t}}{\sqrt{2\pi}}e^{-z^2/2} + o(w)
\end{equation}
\end{theorem}

\begin{remark}
The value of $w$ is sufficiently small when the uncertainty level $\sigma$ is sufficiently large compared to prize-cost ratio $\theta/c_{i(j)}$. 
\end{remark}

In equation (\ref{eq-equilibrium-effort}), the variables $w_{i(j)}$ measure the abilities of two players, while $\rho_{i(j)}$ normalizes $w_{i(j)}$ into the interval $(0, 1)$. 
Specifically, $\rho_{i(k)}$ and $w_{i(j)}$ are in a strictly increasing bijective relationship. 
It is not hard to see that function $\gamma(\cdot)$ is strictly increasing on $(-1,1)$, ranging from $-\infty$ to $+\infty$. 
The function $\rho(\cdot)$ is strictly increasing on $\mathbb{R}$, ranging from $-1$ to $1$. 
%% Forms
The equilibrium effort $m_{i(j)}$ can be represented to the product of two components:
the normal density function $\phi(y; 0, \sigma^2(T-t))$, which represents the probability density of a normal distribution with mean zero and variance $\sigma^2(T-t)$ evaluated at state $y$, and an amplitude factor $K_{i(j)}(z; \theta, \sigma, c_i, c_j) := \frac{\sigma^2}{2}\left[\gamma(\rho_{i}) + \gamma(\rho_{j})\right]\left[1-\rho(z)^2\right]\left[1 \pm \rho(z)\right]$. 
The normal density governs the concentration of competitive intensity over state, i.e., perceived output gap $\tilde{y}_t$, while the amplitude term $K_{i(j)}$ modulates the asymmetry (or skewness) of effort allocation between players.

It is also evident that the parameters $\theta$, $c_i$ and $c_j$ influence equilibrium effort exclusively through the amplitude component.
In contrast, the effect of $\sigma$ is more nuanced, as it enters both the normal density and amplitude terms. 
Based on the structure of (\ref{eq-equilibrium-effort}), we further conclude that the equilibrium effort level is \textit{not} uniformly increasing in the prize-cost ratio $\theta/c_{i(j)}$ across all states $\tilde{y}$—particularly for laggard states.
The uncertainty term $\sigma$ and the remaining time $T - t$ make the equilibrium effort more dispersed: under high uncertainty or with ample remaining time, players exert higher effort in extreme states and lower effort in central states.
As time progresses and the deadline approaches, outcomes become more predictable, and effort becomes increasingly concentrated around the pivot state.

For more properties of the equilibrium, please refer to \citet{ryvkin2022fight}. 
Here, we only provide a supplementary analysis related to contest design:

@@

In online crowdsourcing contests, designers typically control key decision variables such as the prize amount $\theta$ (we exclude more complex prize structures in this study), the contest duration $T$, and the signal precision $\lambda$. 
A key concern is that these variables may act as substitutes—implying that the optimal choice of one may alter or offset the optimal choices of the others.

A first observation is that the signal precision $\lambda$ does not influence the total expected effort $M(\tilde{y}_t, t)$.
Under the simplifying assumption that $S_t = \bar{S}$ is constant, the incorporation of signals does not reduce overall uncertainty.
As a result, the evolution of the filtered state $\tilde{y}_t$ in (\ref{filtered-x}) does not lead to an increase in $M(\tilde{y}_t, t)$ compared to the unfiltered state $y_t$ specified in (\ref{eq-state-dynamics}).\footnote{
However, this result primarily reflects the limitations of our model.
In a more general setting with fewer restrictions, the signal precision parameter $\lambda$ would clearly affect the structure of $M$,
although such cases are beyond the scope of this paper.
}

Next, we turn to the other two design variables.
When the two contestants are of similar strength, i.e., $c_i = c_j = c$, the total expected effort admits a particularly simple approximation, as shown in equation (\ref{eq-totaleffort-reduced}).
Suppose the contest designer’s objective takes the form $\beta^{T}M(\tilde{y}_0, 0)^\alpha - \theta$ for some $0 < \alpha < 1$ and $0 < \beta \le 1$,
it is straightforward to show that this objective function is jointly concave in $(\theta, T)$.
